### 2014-11-13 tex/intro.tex
Restored paragraph

Unfortunately, value sets often do not support aliasing and require a
recursive definition of objects~\cite{..}. Also, heap updates often
require that the path constraint be rewritten to reflect the update,
and the constraints in the value set may also need to be rewritten with the
addition of auxiliary variables. These non-local operations make it
difficult to use value sets in symbolic execution. As is
typical in static analysis, over approximation of the value sets
alleviates some of the limitations but also leads to false positives.

>>>>

Some of these
previous attempts, however, are unable to handle aliasing in heaps due
to a recursive definition of objects~\cite{..}, while others require a
set of heaps as input and are unable to initialize heaps
on-the-fly~\cite{..}. For these reasons the techniques use
over-approximations to reason about heaps and may report false
positives. Also, update to heaps require a rewrite of the constraint
system making it prohitive for use in the context of symbolic
execution.

\begin{comment}
Unfortunately, value sets often do not support aliasing and require a
recursive definition of objects~\cite{..}. Also, heap updates often
require that the path constraint be rewritten to reflect the update,
and the constraints in the value set may also need to be rewritten with the
addition of auxiliary variables. These non-local operations make it
difficult to use value sets in symbolic execution. As is
typical in static analysis, over approximation of the value sets
alleviates some of the limitations but also leads to false positives.
\end{comment}
